Test 1

### 2020-11-12 DATA622/Test1.rmd
Minor changes
More work on Test 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Use the dataset you used for HW-1 (Blue/Black)
# 
# (A) Run Bagging (ipred package)   
# 
#   -- sample with replacement
# 
#   -- estimate metrics for a model
# 
#   -- repeat as many times as specied and report the average
# 
# (B) Run LOOCV (jacknife) for the same dataset
# 
# --- iterate over all points
# 
#      -- keep one observation as test
# 
#     -- train using the rest of the observations
# 
#     -- determine test metrics
# 
#     -- aggregate the test metrics
# 
# end of loop
# 
# find the average of the test metric(s)
# 
# Compare (A), (B) above with the results you obtained in HW-1  and write 3 sentences explaining the
# 
# observed difference.
# 
# You can implement it in java/spark, python or R.
# 
# Submit RMD or PDF and the python/R scripts.
# 
# --
# 
# i would recommend that you implement it from scratch but you may use any package. It is not a requirement.
# 
# bagging is available in ipred package in R.
```
This test is an extension of the work done in Homework 1.  I will be extending it with bagging and leave one out cross-validation (LOOCV), and adding in the results into the evaluation of the algorithms.

## Preliminaries

@@

Again these results are highly dependent on the underling data, and additional runs should be done in order to ensure the conclusions are real and not soley based on idiosyncrasies in the data.  The idea is inline with what has been taught in this class.

>>>>

**Available Online at: [https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA622/Test1.rmd](https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA622/Test1.rmd)**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
## Preliminaries
This test is an extension of the work done in Homework 1.  I will be extending it with bagging and leave one out cross-validation (LOOCV), and adding in the results into the evaluation of the algorithms.

@@
